---
title: "Replication"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This document allows an easy replication of the main results of this research. To run correctly, the project folder has to be copied with the same structure as the original and the working directory set to the location of this local copy. The next step is to load the required packages, as well as two own functions to save images and my theme style.

```{r working directory and packages}
setwd("C:/Users/Prol/Documents/R/wd/covid")

library(tidyverse)
library(gganimate)
library(zoo)
library(forecast)
library(fable)
library(ggplot2)
library(tsibble)
library(feasts)
library(lubridate)
library(opera)
library(ggExtra)
library(mgcv)
library(timeDate)
library(lmtest)
library(devtools)
library(EIAdata) # install_github("Matt-Brigida/EIAdata", force = T) # dev. version
library(xts)
library(plm)
library(directlabels)
library(gtable)
library(gridExtra)
library(viridis)
library(scales)
library(broom)
library(data.table)
library(sandwich)
library(plotly)
library(gganimate)
library(ggrepel)

write.png<- function(object, filename, width=5, height=4, pointsize=12, res=300){
  png(filename= filename, type="cairo",units="in", width=width,
      height=height, pointsize=pointsize, res=res)
  plot(object)
  dev.off()
  object
}

mytheme <- function(base_size = 12, base_family = ""){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.border     = element_blank(),
      axis.line        = element_blank(),
      axis.ticks = element_line(color = "grey"),
      panel.grid.major = element_line(),
      panel.grid.major.x = element_line(colour = "grey", size = 0.1, linetype = "dotted"),
      panel.grid.major.y = element_line(colour = "grey", size = 0.1, linetype = "dotted"),
      panel.grid.minor = element_line(),
      panel.grid.minor.x = element_line(colour = "grey", size = 0.1, linetype = "dotted"),
      panel.grid.minor.y = element_line(colour = "grey", size = 0.1, linetype = "dotted"),
      strip.background = element_blank(),
      legend.key       = element_blank()
    )
}
```

# Import data

The original data, both electricity consumption and temperature, were in subdaily resolution. We load here the full dataset already converted to daily values, and including also the country-specific holidays dummy. See the original script covid.R for more details on data pre-processing. 

```{r data}
ddata<- readRDS("./data/clean/ddata2.rds") %>% unique() %>% filter(date < "2020-08-01")
```


# Define the dynamic harmonic regression and forecast

The function "get_arima_results()" contains the whole analysis, that can be divided in the following steps: (1) Filter data for the specific country and divide it into two datasets: "train" contains all the data until February 2020 included, and "test" contains the data to produce the forecast from March 2020. (2) The datasets are converted to time series format with multiple weekly and yearly seasonality levels. (3) Box-Cox transformation. (4) Calculate Fourier terms. (5) Run the ARIMA model. (6) Calculate the fourier terms for the forecast period. (7) Estimate the forecast. (8) Save results.

```{r define regression}
get_arima_results<- function(where = "ES", k = NULL, j = 3, p = 1, d = 1, q = 1){ # if k is set no automatic selection (which takes long time)
  
  # (1) import data for the specific country
  train<- ddata %>% filter(country == where, date < "2020-03-01") %>% na.omit()
  test<- ddata %>% filter(country == where, date >= "2020-03-01") %>% na.omit()
  
  # (2) convert into multiple (weekly and yearly) seasonality time series (msts)
  train_msts<- msts(train$load, seasonal.periods = c(7, 365.25))
  test_msts<- msts(test$load, seasonal.periods = c(7, 365.25)) %>% na.omit()
  
  # (3) Box-Cox transformation
  lambda<- BoxCox.lambda(train_msts)
  
  # (4) fourier term
  harmonic<- fourier(train_msts, K = c(j, k))
  
  # (5) run model
  fit <- Arima(train_msts, 
               xreg = cbind(train$max_temp, train$max_temp^2,
                            as.factor(train$holiday), harmonic),
               lambda = lambda, order = c(p,d,q))
  
  # (6) forecast fourier term 
  test_harmonic<- fourier(train_msts, K = c(j, k), h = length(test_msts))
  
  # (7) forecast
  fct<- forecast(fit, xreg = cbind(test$max_temp, test$max_temp^2,
                                   as.factor(test$holiday), test_harmonic))
  
  # (8) save results
  result<- data.frame(date = test$date,
                      actual = test$load,
                      fct = as.numeric(fct$mean),
                      low80 = as.numeric(fct$lower[, 1]),
                      low95 = as.numeric(fct$lower[, 2]),
                      up80 = as.numeric(fct$upper[, 1]),
                      up95 = as.numeric(fct$upper[, 2])) %>%
    mutate(dif = (100*(actual-fct))/actual,
           diflow80 = (100*(actual-low80))/actual,
           diflow95 = (100*(actual-low95))/actual,
           difup80 = (100*(actual-up80))/actual,
           difup95 = (100*(actual-up95))/actual,
           country = where) %>% as_tibble()
  
  mylist<<- list(fit = fit, 
                 forecast = fct, 
                 k = k,
                 lambda = lambda,
                 train = train, 
                 test = test,
                 result = result)
  
  saveRDS(mylist, paste("./data/results/forecast_manual/results_", where, ".rds", sep = ""))
  
  return(round(c(k, lambda),2))
}
```

# Get country-specific results

First we create a list where the results will be saved within the function and define the colors that will be used in the figures

```{r create list and color vector}
mylist<- list()
viridis_col<- c("#440154FF", "#472D7BFF", "#3B528BFF", "#2C728EFF", "#21908CFF",
                "#27AD81FF", "#5DC863FF", "#AADC32FF", "#FDE725FF")
```

We run the "get_arima_results()" function defined in the previous section specifying the country (argument where) with the 2-letter country code, the Fourier (j,k) and the ARIMA(p,d,q) orders. The results of this function are saved in  "./data/results/forecast_manual/results_CountryCode.rds", so it can be then imported with the function readRDS. Note that when you clone the github repository you already have all the results and figures saved. Running this code will overwrite the previous files.

For each country you get (1) the residual dignostics, (2) the main regression results, (3) 

```{r run regression AT}
# run ARIMA model for Austria
get_arima_results(where = "AT", j = 3, k = 9, p = 0, d = 1, q = 4)


# import results
atlist<- readRDS("./data/results/forecast_manual/results_AT.rds")
at_fit<- atlist$fit

# see residuals and coeftests
checkresiduals(at_fit)
coeftest(at_fit)

# Plot differences
at_result<- atlist$result %>% mutate(wday = weekdays(date))
at_result$lockdown<- as.Date("2020-03-16")

sunday<- at_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
atplot<- ggplot(at_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[7], alpha = .2) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[7], alpha = .15) +
  geom_line(color = viridis_col[7]) + geom_point(color = viridis_col[7]) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-16"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-16"), y = -25, label = "(1)") +
  # annotate("text", x = as.Date("2020-03-02"), y = -33, label = "-8%", color = "#21908CFF", hjust = 0) +
  #•annotate("text", x = as.Date("2020-03-02"), y = -33, label = "2.9*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-25, 20)) +
  labs(x = element_blank(), y = element_blank(), title = "Austria") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(atplot, "./figures/at.png")

# Plot absolute values
atplot2<- ggplot(at_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[7], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-16"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-16"), y = .1, label = "(1)") +
  labs(x = element_blank(), y = element_blank(), title = "Austria") +
  coord_cartesian(ylim= c(.1, .2)) +
  scale_y_continuous(breaks = c(.1, .2)) +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(atplot2, "./figures/at2.png")
```

This same process is repeated for all individual countries.

```{r run regression all other countries/states}
############# 4.2 CA ############
# arima
get_arima_results(where = "CA", j = 3, k = 3, p = 4, d = 1, q = 3)
calist<- readRDS("./data/results/forecast_manual/results_CA.rds")


ca_fit<- calist$fit
checkresiduals(ca_fit)
coeftest(ca_fit)

ca_result<- calist$result
ca_result$lockdown<- as.Date("2020-03-19")

sunday<- ca_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
caplot<- ggplot(ca_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[6], alpha = .2) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[6], alpha = .15) +
  geom_line(color = viridis_col[6]) + geom_point(color = viridis_col[6]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-19"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-19"), y = -35, label = "(1)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -23, label = "1.8*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-35, 10)) +
  labs(x = element_blank(), y = element_blank(), title = "California") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(caplot, "./figures/ca.png")

caplot2<- ggplot(ca_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[6], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-19"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-19"), y = .5, label = "(1)") +
  labs(x = element_blank(), y = element_blank(), title = "California") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(caplot2, "./figures/ca2.png")



############# 4.3 DE ############
get_arima_results(where = "DE", j = 3, k = 11, p = 4, d = 1, q = 1) # get_results2(where = "DE")
delist<- readRDS("./data/results/forecast_manual/results_DE.rds")

de_fit<- delist$fit
checkresiduals(de_fit)
coeftest(de_fit)

de_result<- delist$result
de_result$lockdown<- as.Date("2020-03-22")

sunday<- de_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
deplot<- ggplot(de_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[5], alpha = .2) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[5], alpha = .15) +
  geom_line(color =viridis_col[5]) + geom_point(color = viridis_col[5]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-22"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-22"), y = -35, label = "(1)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -23, label = "1.8*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-35, 10)) +
  labs(x = element_blank(), y = element_blank(), title = "Germany") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(deplot, "./figures/de.png")

deplot2<- ggplot(de_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[5], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-22"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-22"), y = .8, label = "(1)") +
  labs(x = element_blank(), y = element_blank(), title = "Germany") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(deplot2, "./figures/de2.png")

############# 4.4 ES ############
get_arima_results(where = "ES", j=3, k = 23, p = 3, d = 1, q = 2)
eslist<- readRDS("./data/results/forecast_manual/results_ES.rds")

es_fit<- eslist$fit
checkresiduals(es_fit)
coeftest(es_fit)

es_result<- eslist$result
es_result$lockdown<- as.Date("2020-03-15")


sunday<- es_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
esplot<- ggplot(es_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[4], alpha = .2) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[4], alpha = .15) +
  geom_line(color = viridis_col[4]) + geom_point(color = viridis_col[4]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-15"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-03-30"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-04-14"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-15"), y = -35, label = "(1)") +
  annotate("text", x = as.Date("2020-03-30"), y = -35, label = "(2)") +
  annotate("text", x = as.Date("2020-04-14"), y = -35, label = "(3)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -43, label = "1.63*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-35, 10)) +
  labs(x = element_blank(), y = element_blank(), title = "Spain") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(esplot, "./figures/es.png")

esplot2<- ggplot(es_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[4], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-15"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-03-30"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-04-14"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-15"), y = .45, label = "(1)") +
  annotate("text", x = as.Date("2020-03-30"), y = .45, label = "(2)") +
  annotate("text", x = as.Date("2020-04-14"), y = .45, label = "(3)") +
  labs(x = element_blank(), y = element_blank(), title = "Spain") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(esplot2, "./figures/es2.png")


############# 4.5 FL ############
get_arima_results(where = "FL", j = 3, k = 3, p = 1, d = 1, q = 2) # get_results2(where = "FL") 
fllist<- readRDS("./data/results/forecast_manual/results_FL.rds")

fl_fit<- fllist$fit
checkresiduals(fl_fit)
coeftest(fl_fit)

fl_result<- fllist$result
fl_result$lockdown<- as.Date("2020-04-03")

sunday<- fl_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
flplot<- ggplot(fl_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[9], alpha = .25) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[9], alpha = .2) +
  geom_line(color = viridis_col[9], size = 1) + geom_point(color = viridis_col[9], size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-04-03"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-04-03"), y = -25, label = "(1)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -23, label = "2.71*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-25, 20)) +
  labs(x = element_blank(), y = element_blank(), title = "Florida") + 
  mytheme()+ theme(plot.title = element_text(hjust = 0.5))

write.png(flplot, "./figures/fl.png")

flplot2<- ggplot(fl_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[9], size = 1) +
  geom_vline(xintercept = as.Date("2020-04-03"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-04-03"), y = .45, label = "(1)") +
  labs(x = element_blank(), y = element_blank(), title = "Florida") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(flplot2, "./figures/fl2.png")

############# 4.6 FR ############
get_arima_results(where = "FR", j = 3, k = 19, p = 7, d = 1, q = 6)
frlist<- readRDS("./data/results/forecast_manual/results_FR.rds")


fr_fit<- frlist$fit
checkresiduals(fr_fit)
coeftest(fr_fit)

fr_result<- frlist$result
fr_result$lockdown<- as.Date("2020-03-17")

sunday<- fr_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
frplot<- ggplot(fr_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[3], alpha = .2) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[3], alpha = .15) +
  geom_line(color = viridis_col[3]) + geom_point(color = viridis_col[3]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-17"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-17"), y = -45, label = "(1)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -43, label = "2.29*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-45, 10)) +
  labs(x = element_blank(), y = element_blank(), title = "France") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(frplot, "./figures/fr.png")

frplot2<- ggplot(fr_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[3], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-17"), linetype = "dotted") +
  labs(x = element_blank(), y = element_blank(), title = "France") +
  annotate("text", x = as.Date("2020-03-17"), y = .9, label = "(1)") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(frplot2, "./figures/fr2.png")


############# 4.7 GB ############
get_arima_results(where = "GB",j = 3, k = 3, p = 2, d = 1, q = 1) # get_results2(where = "UK")
gblist<- readRDS("./data/results/forecast_manual/results_GB.rds")

gb_fit<- gblist$fit
checkresiduals(gb_fit)
coeftest(gb_fit)

gb_result<- gblist$result
gb_result$lockdown<- as.Date("2020-03-23")

sunday<- gb_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
gbplot<- ggplot(gb_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[1], alpha = .2) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[1], alpha = .15) +
  geom_line(color = viridis_col[1]) + geom_point(color = viridis_col[1]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-23"), y = -45, label = "(1)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -33, label = "2.05*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-45, 10)) +
  labs(x = element_blank(), y = element_blank(), title = "Great Britain") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(gbplot, "./figures/gb.png")

gbplot2<- ggplot(gb_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[1], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "dotted") +
  labs(x = element_blank(), y = element_blank(), title = "Great Britain") +
  annotate("text", x = as.Date("2020-03-23"), y = .5, label = "(1)") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(gbplot2, "./figures/gb2.png")

############# 4.8 IT ############
get_arima_results(where = "IT", j = 3, k = 20, p = 3, d = 1, q = 1) 
itlist<- readRDS("./data/results/forecast_manual/results_IT.rds")

it_fit<- itlist$fit
checkresiduals(it_fit)
coeftest(it_fit)

it_result<- itlist$result
it_result$lockdown<-  as.Date("2020-03-10")

sunday<- it_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
itplot<- ggplot(it_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), alpha = .1, fill = viridis_col[2]) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), alpha = .05, fill = viridis_col[2]) +
  geom_line(color = viridis_col[2]) + geom_point(color = viridis_col[2]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-10"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-03-21"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-04-14"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-10"), y = -45, label = "(1)") +
  annotate("text", x = as.Date("2020-03-21"), y = -45,label = "(2)") +
  annotate("text", x = as.Date("2020-04-14"), y = -45, label = "(3)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -43, label = "2.33*", hjust = 0) +
  geom_segment(aes(x = as.Date("2020-05-17"), y = -13, xend = as.Date("2020-05-17"),
                   yend = -30), color = "darkgrey") +
  annotate("text", x = as.Date("2020-05-17"), y = -32, label = "Sunday",  color = "darkgrey") +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-45, 10)) +
  labs(x = element_blank(), y = element_blank(), title = "Italy") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(itplot, "./figures/it.png")

itplot2<- ggplot(it_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[2], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-10"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-03-21"), linetype = "dotted") +
  geom_vline(xintercept = as.Date("2020-04-14"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-10"), y = .41, label = "(1)") +
  annotate("text", x = as.Date("2020-03-21"), y = .41,label = "(2)") +
  annotate("text", x = as.Date("2020-04-14"), y = .41, label = "(3)") +
  labs(x = element_blank(), y = element_blank(), title = "Italy") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(itplot2, "./figures/it2.png")

############# 4.9 NY ############
get_arima_results(where = "NY", j = 3, k = 5, p = 3, d = 1, q = 1) 
nylist<- readRDS("./data/results/forecast_manual/results_NY.rds")


ny_fit<- nylist$fit
checkresiduals(ny_fit)
coeftest(ny_fit)

ny_result<- nylist$result
ny_result$lockdown<- as.Date("2020-03-22")

sunday<- ny_result %>% mutate(wday = weekdays(date)) %>% filter(wday == "Sunday")
nyplot<- ggplot(ny_result, aes(date, dif)) +
  geom_ribbon(aes(date, ymin = diflow80, ymax = difup80), fill = viridis_col[8], alpha = .25) +
  geom_ribbon(aes(date, ymin = diflow95, ymax = difup95), fill = viridis_col[8], alpha = .2) +
  geom_line(color = viridis_col[8]) + geom_point(color = viridis_col[8]) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = as.Date("2020-03-22"), linetype = "dotted") +
  annotate("text", x = as.Date("2020-03-22"), y = -25, label = "(1)") +
  #annotate("text", x = as.Date("2020-03-02"), y = -32, label = "1.63*", hjust = 0) +
  geom_point(data = sunday, aes(date, dif), color = "darkgrey", size = 1.5) +
  coord_cartesian(ylim = c(-25, 20)) +
  labs(x = element_blank(), y = element_blank(), title = "New York") + 
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(nyplot, "./figures/ny.png")

nyplot2<- ggplot(ny_result, aes(date, fct)) +
  geom_line(size = .5) +
  geom_ribbon(aes(date, ymin = low80, ymax = up80), alpha = .12) +
  geom_ribbon(aes(date, ymin = low95, ymax = up95), alpha = .08) +
  geom_line(aes(date, actual),  color = viridis_col[8], size = 1) +
  geom_vline(xintercept = as.Date("2020-03-22"), linetype = "dotted") +
  labs(x = element_blank(), y = element_blank(), title = "New York") +
  annotate("text", x = as.Date("2020-03-22"), y = .31, label = "(1)") +
  mytheme() + theme(plot.title = element_text(hjust = 0.5))

write.png(nyplot2, "./figures/ny2.png")
```


# Cumulative electricity decline

After calculating the difference in electricity consumption with respect to the baseline, we can calculate the cumulative decline by country.

```{r Cumulative electricity decline}
atc<- at_result %>% filter(date >= "2020-03-15") %>% mutate(t = 0:(length(date)-1))
cac<- ca_result %>% filter(date >= "2020-03-18") %>% mutate(t = 0:(length(date)-1))
dec<- de_result %>% filter(date >= "2020-03-21") %>% mutate(t = 0:(length(date)-1))
esc<- es_result %>% filter(date >= "2020-03-13") %>% mutate(t = 0:(length(date)-1))
flc<- fl_result %>% filter(date >= "2020-04-02") %>% mutate(t = 0:(length(date)-1))
frc<- fr_result %>% filter(date >= "2020-03-16") %>% mutate(t = 0:(length(date)-1))
gbc<- gb_result %>% filter(date >= "2020-03-22") %>% mutate(t = 0:(length(date)-1))
itc<- it_result %>% filter(date >= "2020-03-09") %>% mutate(t = 0:(length(date)-1))
nyc<- ny_result %>% filter(date >= "2020-03-21") %>% mutate(t = 0:(length(date)-1))

cum_results<- bind_rows(atc, cac, dec, esc, flc, frc, gbc, itc, nyc) %>%
  arrange(country, t) %>% select(country, t, date, actual, fct, dif) %>%
  group_by(country) %>% 
  mutate(index = 100*cumsum(actual)/cumsum(fct),
         index = ifelse(t == 0, 100, index),
         index_pc = index-100)
  
saveRDS(cum_results, "./data/results/cum_results.rds")
cum_results<- readRDS("./data/results/cum_results.rds")

legend<- cum_results %>% summarize(t = max(t), index = last(index), index_pc = last(index_pc))
legend %>% arrange(index_pc)
my_colors <- RColorBrewer::brewer.pal(4, "Blues")[2:4]

cumplot<- ggplot(cum_results, aes(t, index_pc, color = fct_reorder(country, index, .fun='last'))) +
  geom_line(size = 1, alpha = 1.5) + 
  geom_point(data = legend, aes(x = t, y = index_pc)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_text_repel(data = legend, aes(x = t, y = index_pc, label = country),
            nudge_x = 5, size = 4, fontface = "bold") +
  scale_color_viridis_d() +
  scale_y_continuous(sec.axis = sec_axis(~ .)) +
  labs(x = "Days from lockdown", y = "Cumulative consumption change (%)") +
  mytheme() + theme(legend.position = "none")

write.png(cumplot, "./figures/cumulative.png")
```


# Stringency

Finally, the relationship between measures stringency and electricity consumption decline is calculated as follows:

```{r Stringency}
# import and clean country- and state-level stringency data
stringencyEU<- read.csv("./data/raw/stringency/OxCGRT_latest.csv") %>%
  select(country = CountryName, date = Date, school = C1_School.closing, school_general = C1_Flag,
         workplace = C2_Workplace.closing, workplace_general = C2_Flag,
         events = C3_Cancel.public.events, events_general = C3_Flag,
         transport = C5_Close.public.transport, transport_general = C5_Flag,
         stayhome = C6_Stay.at.home.requirements, stayhome_general = C6_Flag,
         movement = C7_Restrictions.on.internal.movement, movement_general = C7_Flag,
         travel = C8_International.travel.controls,
         index = StringencyIndex) %>%
  filter(country %in% c("Germany", "Spain", "Italy", "France", "Austria", "United Kingdom")) %>%
  droplevels() %>%
  mutate(country = as.factor(country),
         date = ymd(date),
         school = as.factor(replace_na(ifelse(school_general == 1 & school == 3, 1, 0), 0)),
         workplace = as.factor(replace_na(ifelse(workplace_general == 1 & workplace == 3, 1, 0), 0)),
         events = as.factor(replace_na(ifelse(events_general == 1 & events == 2, 1, 0), 0)),
         transport = as.factor(replace_na(ifelse(transport_general == 1 & transport == 2, 1, 0), 0)),
         stayhome = as.factor(replace_na(ifelse(transport_general == 1 & stayhome == 3, 1, 0), 0)),
         movement = as.factor(replace_na(ifelse(movement_general == 1 & movement == 2, 1, 0), 0)),
         travel = as.factor(replace_na(ifelse(travel == 4, 1, 0), 0))) %>%
  select(country, date, school, workplace, events, transport, movement, travel, index) %>%
  arrange(country, date) %>% as_tibble()

stringencyEU$country<- plyr::mapvalues(stringencyEU$country,
              from = c("Germany", "Spain", "Italy", "France", "Austria", "United Kingdom"),
              to = c("DE", "ES", "IT", "FR", "AT", "GB"))


stringencyUS<- read.csv("./data/raw/stringency/OxCGRT_US_states_temp.csv") %>%
  select(country = RegionName, date = Date, school = C1_School.closing, school_general = C1_Flag,
         workplace = C2_Workplace.closing, workplace_general = C2_Flag,
         events = C3_Cancel.public.events, events_general = C3_Flag,
         transport = C5_Close.public.transport, transport_general = C5_Flag,
         stayhome = C6_Stay.at.home.requirements, stayhome_general = C6_Flag,
         movement = C7_Restrictions.on.internal.movement, movement_general = C7_Flag,
         travel = C8_International.travel.controls,
         index = StringencyIndex) %>%
  filter(country %in% c("California", "New York", "Florida")) %>%
  droplevels() %>%
  mutate(country = as.factor(country),
         date = ymd(date),
         school = as.factor(replace_na(ifelse(school_general == 1 & school == 3, 1, 0), 0)),
         workplace = as.factor(replace_na(ifelse(workplace_general == 1 & workplace == 3, 1, 0), 0)),
         events = as.factor(replace_na(ifelse(events_general == 1 & events == 2, 1, 0), 0)),
         transport = as.factor(replace_na(ifelse(transport_general == 1 & transport == 2, 1, 0), 0)),
         stayhome = as.factor(replace_na(ifelse(transport_general == 1 & stayhome == 3, 1, 0), 0)),
         movement = as.factor(replace_na(ifelse(movement_general == 1 & movement == 2, 1, 0), 0)),
         travel = as.factor(replace_na(ifelse(travel == 4, 1, 0), 0))) %>%
  select(country, date, school, workplace, events, transport, movement, travel, index) %>%
  arrange(country, date) %>% as_tibble()

stringencyUS$country<- plyr::mapvalues(stringencyUS$country,
              from = c("California", "Florida", "New York"),
              to = c("CA", "FL", "NY"))

stringency<- bind_rows(stringencyEU, stringencyUS)


# import consumption data
dif_results<- readRDS("./data/results/dif_results.rds") %>%
  select(country, date, dif) %>% mutate(country = as.factor(country))

# merge data
str_data<- right_join(dif_results, stringency, by = c("country", "date")) %>%
  mutate(country = as.factor(country)) %>% na.omit() %>% droplevels()

# median for country labels
medpoint<- str_data %>% group_by(country) %>%
  summarise(dif = median(dif), index = median(index))

# color palette
# order: AT, CA, DE, ES, FL, \newline FR, GB, IT, NY
mycolors = c(viridis_col[7], viridis_col[6],viridis_col[5], viridis_col[4], viridis_col[9],
             viridis_col[3], viridis_col[1], viridis_col[2], viridis_col[8])

# plot
strindexplot<- ggplot(str_data, aes(index, dif)) +
  geom_point(aes(color = country), alpha = .15) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
  geom_smooth(method = loess, se = F, color = "black", size = 1) +
  geom_text_repel(data = medpoint, aes(x = index, y = dif, color = country, label = country), 
            fontface = "bold", size = 4.5, force = .01) +
  scale_color_manual(values = mycolors) +
  scale_y_continuous(sec.axis = sec_axis(~ .)) +
  labs(x = "Stringency index", y = "Decrease daily consumption (%)") +
  mytheme() + theme(aspect.ratio = 1, legend.position = "none")

write.png(strindexplot, "./figures/stringency_index.png", width=5, height=5)
```

